---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# usportsR

<!-- badges: start -->
[![R-CMD-check](https://github.com/uwaggs/usportsR/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/uwaggs/usportsR/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

`usportsR` is a package that is designed to provide users with data from all Usports
sanctioned sports.

- The package contains U Sports data spanning over a decade of pre-season, regular season, and post-season matches.

- Sports currently included are Soccer, Basketball, Ice Hockey, Field Hockey, Track and Field
Field Hockey, Football, Wrestling, Swimming and Rugby

- We currently provide access to box score, play-by-play, schedules and rankings data 

## Installation

You can install the development version of usportsR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("uwaggs/usportsR")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(usportsR)
library(dplyr)
## basic example to find number of 40+ point games in the last decade

mens_player_box_scores <- basketball_player_box_score("m",c(2023,2022,2021,2019,2018,2017,2016,2015,2014))
mens_40_pt_games <- mens_player_box_scores %>% filter(pts >= 40)
head(mens_40_pt_games,10)
```

```{r}
library(ggplot2)
## simple plot to illustrate points vs assists in 40+ point games in Usport basketball games

ggplot(mens_40_pt_games,aes(x = pts,y = ast)) + geom_point() +
  labs(title = "Points Vs Assists in 40 point games", x = "Points",y = "Assists")

```


